\documentclass{article}
\usepackage{graphicx}
\begin{document}

\begin{center}
{\Huge \textbf{Interactive Systems H}}//
{\huge \textbf{Design Checkpoint}}//
\vspace{5mm}
Dominic Small 2195530s\\
Michelle Dove 2142931d\\
Alistair\\
\end{center}

\section{Project Concept}
\label{sec:project}
Our project is a GPX viewing web app for runners who are looking to improve their fitness through ananlysis of data of previous runs from fitness trackers. It will allow them to look at previous times for a given route and how that has changed, as well as examining variables like the elevation change for that route. Runners can upload files and see the various stats from these runs, as well as share them with friends on social media.

It is also possible for runners to create routes for them to run using this app. This can give them information such as the time an average runner would take, giving them a goal to strive for. This information can also show a runner that they may not be ready for a run of this length, leading them to try a more approriate run. This average time can be compared to all their previous times in a graph, allowing the runners to see when they beat it.

Any skill level of runner could use this app, although it is aimed more at casual runners than professionals. However, anyone within this range (from a completely new runner to someone who does occaisional marathons) will find a use for it. Since it is aimed at helping runners improve themselves, those just starting out will probably find the most use for it, which will hopefully continue as they develop.

\end{document}
